Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-05-23 bibat/examples/baseball/docs/report.qmd
Update vignette

The first step in preparing data is to decide what prepared data looks like for
the purposes of our analysis. Bibat provides dataclasses called `PreparedData`
and `MeasurementsDF` to help get started with this, which I found in the file
`baseball/prepared_data.py`.

@@

```{.python include="../baseball/data_preparation.py" start-line=125}
```

@@

I started by defining some Stan input functions that pass arbitary prepared
data on to each of the models:

@@

Note that:
* The Stan file, prepared data folder and stan input function are referred to by
  strings. The analysis should raise an error if you enter a non-existing value.
* Both inferences are set to run in "prior" and "posterior" modes - the other
  pre-defined mode is "kfold", but you can also write your own!
* You can enter arbitrary arguments to cmdstanpy's `CmdStanModel.sample` method
  in the `[sample_kwargs]` table.
* You can enter mode-specific overrides in `[sample_kwargs.<MODE>]`. This can be
  handy if you want to run more or fewer iterations for a certain mode.

@@

Now that the inferences are ready it's time to check them out. Bibat provides a
jupyter notebook at `baseball/investigate.ipynb` for exactly this purpose.

A lot of code from the example analysis's notebook was reusable, so I largely
followed its structure, with a few tweaks.

@@

>>>>

The first step in preparing data is to decide what prepared data looks like for
the purposes of our analysis. Bibat provides dataclasses called `PreparedData`
and `MeasurementsDF` to help get started with this, which I found in the file
`baseball/data_preparation.py`.

@@

```{.python include="../baseball/data_preparation.py" start-line=101}
```

I had to update the `prepare_data` function to take into account the
two raw data sources:

```{.python include="../baseball/data_preparation.py" start-line=33 end-line=52}
```

To finish off I deleted the unused global variables `MEASUREMENTS_FILE`,
`NEW_COLNAMES`, `DROPNA_COLS` and `DIMS`, then checked if the function
`load_prepared_data` needed any changes: I was pretty sure it didn't.

@@

I started by defining some Stan input functions that pass arbitary prepared
data on to each of the models:^[Note that this code uses the scipy function
`logit`, which it imported like this: `from scipy.special import logit`]

@@

Note that:

- The Stan file, prepared data folder and stan input function are referred to by
  strings. The analysis should raise an error if you enter a non-existing value.
- Both inferences are set to run in "prior" and "posterior" modes - the other
  pre-defined mode is "kfold", but you can also write your own!
- You can enter arbitrary arguments to cmdstanpy's `CmdStanModel.sample` method
  in the `[sample_kwargs]` table.
- You can enter mode-specific overrides in `[sample_kwargs.<MODE>]`. This can be
  handy if you want to run more or fewer iterations for a certain mode.

@@

Now that the inferences are ready it's time to check them out. Bibat provides a
Jupyter notebook at `baseball/investigate.ipynb` for exactly this purpose. The
notebook's main job is to create plots and save them in the `plots` directory
when it is executed with the command `jupyter execute investigate.ipynb`, which
is the final step in the chain of commands that is triggered by `make
analysis`.

A notebook is arguably a nicer home for code that creates plots than a plain
python script because it allows for literate documentation and an iterative
workflow. A notebook makes it easy to, for example, add some code to change the
scale of a plot, execute the code and see the new results, then update the
relevant documentation all in the same place.

The code from the example analysis's notebook for loading `InferenceData` was
reusable with a few tweaks to avoid missing file errors, so I kept it. On the
other hand, I wanted to make some different plots from the ones in the example
analysis, including some that required loading prepared data. To check out
everything I did, see
[here](https://github.com/teddygroves/bibat/blob/main/bibat/examples/baseball/baseball/investigate.ipynb).

@@

# Documenting the analysis

The final step was to document my analysis. To do this I edited the file
`docs/report.qmd`, then ran `quarto render docs/report.qmd`, which produced the
very html document that you are probably reading now! You can find the complete
`report.qmd` file
[here](https://github.com/teddygroves/bibat/blob/main/bibat/examples/baseball/docs/report.qmd).
